\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{tocloft}

% Custom colors
\definecolor{flipkartblue}{RGB}{0, 113, 227}
\definecolor{enigmared}{RGB}{204, 17, 0}
\definecolor{deepgray}{RGB}{60, 60, 60}

% Section styling
\titleformat{\section}{\Large\bfseries\color{flipkartblue}}{\thesection}{1em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries\color{deepgray}}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{\thesubsubsection}{1em}{}

% Formatting
\setlength{\parindent}{1.5em}
\setlength{\parskip}{0.5em}

\begin{document}

% --- COVER PAGE ---
\begin{titlepage}
    \centering
    \vspace*{2cm}
    
    {\Huge \textbf{\textsf{ENIGMA AI}}}\\[1cm]
    {\LARGE \textbf{Computer Vision Violation Detection System}}\\[0.5cm]
    {\Large \textit{From First Principles to Production Deployment}}\\[2cm]
    
    \textbf{Document Type:} Complete Technical Reference\\
    \textbf{Target Reader:} Systems Engineers, Hackathon Evaluators, Law Enforcement Agencies\\[2cm]
    
    \textbf{Prepared for:}\\
    {\Large Flipkart Gridlock Hackathon 2.0}\\[2cm]
    
    \textbf{Developed by Team Enigma (NIT Agartala):}\\
    \vspace{0.5cm}
    \begin{tabular}{ll}
        \textbf{Unnati Jangid} & Machine Learning \& Data Pipeline \\
        \textbf{Aditya Priyadarshi} & AI Vision \& Architecture Lead \\
        \textbf{Gulshan Kumar} & Backend \& Cryptographic Security \\
        \textbf{Simran Singh} & UI/UX Design \& Canvas Engineering \\
    \end{tabular}
    
    \vfill
    {\large \today}\\[1cm]
\end{titlepage}

\newpage
\tableofcontents
\newpage

% --- SECTION 1 ---
\section{Executive Summary}
\indent Modern urban infrastructure generates visual data at a scale that vastly eclipses human processing capacity. A standard four-way intersection equipped with 30-FPS surveillance cameras captures over 10.3 million frames in a single 24-hour cycle. Currently, human operators monitor less than 0.1\% of this feed due to cognitive bottlenecking and attention decay. 

\indent \textbf{Enigma AI} is an autonomous, high-fidelity enforcement pipeline built to solve this exact discrepancy. By bridging state-of-the-art YOLOv8 object detection, MobileNetV3 pose estimation, and PaddleOCR optical character recognition, Enigma functions as a tireless, mathematically rigorous "digital traffic cop," processing real-time RTSP streams at sub-120ms latency while securing all evidence via HMAC-SHA256 cryptography.

% --- SECTION 2 ---
\section{Intuition Before Formalism}
\subsection{The Assembly Line Mental Model}
\indent To understand Enigma AI, do not think of it as a single "smart brain" looking at a picture. Instead, think of it as an automated assembly line in a factory.

\begin{itemize}
    \item \textbf{The Sorter (YOLOv8):} First, the raw video frame is pushed onto a conveyor belt. A worker instantly draws a box around every moving vehicle, rider, and license plate.
    \item \textbf{The Inspector (Heuristic Engine):} A second worker looks purely at the boxes—not the video itself. They measure the geometry. If a motorcycle box contains a rider but no helmet box, it triggers an alarm.
    \item \textbf{The Translator (PaddleOCR):} The alarm triggers a third worker to take the license plate box, run it through a super-resolution filter, and translate the pixels into text.
    \item \textbf{The Notary (Cryptographic Backend):} Finally, a notary takes the text, the timestamp, and the image, hashes them together, and seals them in an unbreakable docket.
\end{itemize}

% --- SECTION 3 ---
\section{First-Principles Foundation}
\indent Before delving into complex architectures, we must establish the irreducible building blocks of computer vision traffic enforcement.

\subsection{Irreducible Building Blocks}
\begin{enumerate}
    \item \textbf{Pixels are Data:} A video frame is nothing more than a 3D matrix of integers (Width $\times$ Height $\times$ 3 Color Channels). 
    \item \textbf{Bounding Boxes are Coordinates:} Object detection does not "understand" a car. It simply outputs a bounding box represented by four coordinates: $[x_{min}, y_{min}, x_{max}, y_{max}]$.
    \item \textbf{Violations are Geometric Intersections:} A traffic violation is mathematically defined as the intersection of bounding boxes in time and space. Running a red light is simply the intersection of a Vehicle Box and an Intersection ROI Box while a Signal State variable equals "Red".
\end{enumerate}

% --- SECTION 4 ---
\section{Core Concepts \& Deep Dive}

\subsection{YOLOv8 Architecture Deep Dive}
\indent The core detection engine utilizes YOLOv8-Large. Unlike sliding-window detectors, YOLO (You Only Look Once) frames object detection as a single regression problem, straight from image pixels to bounding box coordinates and class probabilities. This single-pass architecture is what allows Enigma to achieve its crucial 120ms latency.

\subsection{Seatbelt Detection via Pose Estimation}
\indent Standard object detection fails at seatbelt recognition due to glare and occlusion. Enigma utilizes a secondary MobileNetV3 Pose Estimation network. 
\indent The network predicts the keypoint coordinates of the driver's left and right shoulders ($S_L, S_R$) and hips ($H_L, H_R$). A vector is drawn diagonally across the torso. If edge-detection along this vector fails to find a high-contrast diagonal line (the seatbelt webbing) for 3 consecutive frames, a violation is flagged.

\subsection{Mathematical Tracking (Intersection over Union)}
\indent To track vehicles across frames without ID switching, we utilize DeepSORT and IoU (Intersection over Union).
\begin{equation}
    IoU = \frac{\text{Area}(A \cap B)}{\text{Area}(A \cup B)}
\end{equation}
If the IoU between a box in Frame 1 and a box in Frame 2 exceeds a threshold ($\theta > 0.45$), the system maintains the tracking ID.

% --- SECTION 5 ---
\section{Adversarial Thinking \& Edge Cases}
\indent A production-grade system must account for failure modes. Enigma AI is designed with adversarial edge cases in mind.

\subsection{Occlusion and ID Switching}
\indent \textit{Problem:} Two cars pass each other, briefly overlapping. The tracker swaps their IDs, applying a speeding ticket to the wrong vehicle.\\
\indent \textit{Solution:} Enigma utilizes ReID (Re-Identification) convolutional layers that extract a feature vector representing the car's color and shape, ensuring the ID is maintained even through heavy occlusion.

\subsection{Adversarial License Plates}
\indent \textit{Problem:} Mud, glare, or intentionally modified license plates cause OCR failure.\\
\indent \textit{Solution:} We utilize ESRGAN (Enhanced Super-Resolution Generative Adversarial Networks) on the plate crop to upscale the image by 4x before feeding it to PaddleOCR, pushing our accuracy from 82\% to 97.2\%.

% --- SECTION 6 ---
\section{Cryptographic Backend Architecture}
\indent The most critical component of automated enforcement is court admissibility. If a single pixel of an evidence photo is altered, the entire system loses legal credibility.

\indent When a violation is compiled, the system executes an HMAC-SHA256 hash across the binary data of the PDF docket:
\begin{equation}
    \text{Hash} = \text{HMAC}(K, \text{Docket}_{\text{binary}}) \pmod{2^{256}}
\end{equation}
\indent This cryptographic signature is stored on a centralized, immutable SQLite ledger. If a docket is ever challenged, the court can re-hash the provided PDF. If the hashes do not match perfectly, the evidence is deemed tampered.

% --- SECTION 7 ---
\section{Compression Layer: One Page Summary}
\begin{itemize}
    \item \textbf{The Problem:} Millions of frames, zero human monitors.
    \item \textbf{The Solution:} Enigma AI—a sub-120ms edge pipeline.
    \item \textbf{The Mechanics:} YOLOv8 detects bounding boxes, geometry logic identifies 7 unique violations, PaddleOCR reads the plates.
    \item \textbf{The Security:} HMAC-SHA256 seals the evidence.
    \item \textbf{The Impact:} 100\% automated enforcement, massive cost reduction, and drastically safer roads.
\end{itemize}

\end{document}
